Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-04-14 paper/arm.tex
pass over discussion and TOC

\section{Arm}
For simplicity, we restrict to top level parallel composition and ignore
fences\footnote{Fences are not actions in \armeight{}, which complicates the
  theorem statements.}.

>>>>

\section{Arm}
\label{sec:arm}
For simplicity, we restrict to top level parallel composition and ignore
fences\footnote{Fences are not actions in \armeight{}, which complicates the
  theorem statements.}.
